Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-03-23 supplement.tex
More pics in supmat

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_17}.

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_17/example_17/errors.png}
  \caption{An unliked node substitution model}
\end{figure}

@@

\richel{Issue at \url{https://github.com/richelbilderbeek/pirouette_article/issues/66}}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_22/example_22/314/errors.png}
  \caption{Assuming a Yule tree prior on a Yule tree}
\end{figure}

@@

\richel{Issue at \url{https://github.com/richelbilderbeek/pirouette_article/issues/67}}

@@

\richel{depends on https://github.com/richelbilderbeek/pirouette/issues/378}

% \begin{figure}[H]
%   \includegraphics[width=\textwidth]{pirouette_example_26/example_26/314/errors.png}
%   \caption{Assuming a Yule tree prior on a BD tree}
% \end{figure}

>>>>

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_27}.

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_27/errors.png}
  \caption{An unliked node substitution model}
\end{figure}

@@

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_22/errors.png}
  \caption{Assuming a Yule tree prior on a Yule tree}
\end{figure}

@@

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_26/errors.png}
  \caption{Assuming a Yule tree prior on a BD tree}
\end{figure}
